\Title

### 2021-01-26 manuscript/manuscript.tex
Update manuscript/manuscript.tex
Co-authored-by: Santiago Soler <santiago.r.soler@gmail.com>

The resulting grid preserves the high resolution of the original data while
avoiding aliasing artifacts because to the block averaging.
Some parts of the grid are smoother and with reduced amplitude (e.g., some
southwestern parts), which is expected from the upward continuation that was
performed to have the grid at a constant height.
On a modest workstation with 16 cores and 16 Gigabytes of RAM,
estimating the \AustraliaEqlNSources{} coefficients with gradient-boosting took
$\sim 1.3$~hours and the forward modelling step took $\sim 18$~minutes.

>>>>

The resulting grid preserves the high resolution of the original data while
avoiding aliasing artifacts because to the block averaging.
Some parts of the grid are smoother and with reduced amplitude (e.g., some
southwestern parts), which is expected from the upward continuation that was
performed to have the grid at a constant height.
On a modest workstation with 16 cores and 16~Gigabytes of RAM,
estimating the \AustraliaEqlNSources{} coefficients with gradient-boosting took
$\sim 1.3$~hours and the forward modelling step took $\sim 18$~minutes.
